Legal Services Market in Russia: Regional Specialization

### 2025-02-06 legal-companies-regional-specialization/Paper.Rmd
Adjust code and reorganise files for paper about regional specialisation on legal services, #6

---
title: "Legal Services Market in Russia: Regional Specialization"
author: "Pavel O. Syomin"
date: "PhD Student at Perm State University"
output:
  word_document:
    reference: reference.docx
bibliography: biblio.bib
csl: biblio-style.csl
---

@@

```{r imports, include=FALSE, cache = TRUE}
source("Script.R")
```

>>>>

---
title: "Legal Services Market in Russia: Regional Specialization"
author: "Pavel O. Syomin"
date: "PhD Student at Perm State University"
output:
  word_document:
    reference: assets/reference.docx
bibliography: assets/biblio.bib
csl: assets/biblio-style.csl
---

@@

```{r imports, include=FALSE, cache = TRUE}
source("helpers/Script.R")
```
